Evidence accumulation for tackling research waste (Supplement)

### 2020-01-27 Manuscript/MS.Rmd
2nd round review update
Resolve conflict

---
title: "Evidence accumulation for tackling research waste"
csl: nature.csl
output:
  pdf_document:
    fig_caption: yes
  word_document: 
    fig_caption: yes
  html_document: 
    fig_caption: yes
bibliography: bibliography.bib
---

@@

>>>>

---
title: "Evidence accumulation for tackling research waste"
csl: nature.csl
output:
  html_document: 
    fig_caption: yes
  word_document: 
    fig_caption: yes
  pdf_document:
    fig_caption: yes
bibliography: bibliography.bib
---

@@

=======

### 2020-01-27 Manuscript/SuppMat.Rmd
Resolve conflict

---
title: "Evidence accumulation for tackling research waste (Supplement)"
csl: nature.csl
output:
  pdf_document:
    fig_caption: yes
  word_document: 
    fig_caption: yes
  html_document: 
    fig_caption: yes
bibliography: bibliography.bib
---

>>>>

---
title: "Evidence accumulation for tackling research waste (Supplement)"
csl: nature.csl
output:
  html_document: 
    fig_caption: yes
  word_document: 
    fig_caption: yes
  pdf_document:
    fig_caption: yes
bibliography: bibliography.bib
---
